Daemon Analysis across Different Machines

### 2018-10-19 pt_characterization/machine_cons_check/daemon_analysis/paper.tex
Rob's docs

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8} (plugged into the {\em bottom left} power strip) & INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb9}  (plugged into the {\em upper left} power strip)  & INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb10}  (plugged into the {\em upper left} power strip)  & INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb12}  (plugged into the {\em upper right} power strip)  & INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of the INC1, INC16, INC128 data used for histograms\label{tab:exp_notesINCs}}
\end{table}

\begin{table}[htp!]
\centering
{\small
 \begin{tabular}{|l|l|l|l|l||l|l|l|} \hline
 Task & Total & Process & Machine & Min (ms) & Max (ms) & Avg (ms) & \# of Iters\\ \hline
 INC1 &  1,000 & {\tt kslowd000} & {\tt sodb8} & 1 & 1 & 1 & 19 \\ \hline
 &   &  & {\tt sodb9} & 1 & 1 & 1 & 15 \\ \hline
 &   &  & {\tt sodb10} & 1 & 1 & 1 & 19 \\ \hline 
 \hline
  &  & {\tt kslowd001} & {\tt sodb8} & 1 & 1 & 1 & 15 \\ \hline
 &   &  & {\tt sodb9} & 1 & 1 & 1 & 18 \\ \hline
 &   &  & {\tt sodb10} & 1 & 1 & 1 & 15 \\ \hline 
 %&   &  & {\tt sodb12} & 1 & 1 & 1 & 19 \\ \hline 
%  \hline
 \end{tabular}
  }
 \caption{\textbf{The statistics of the daemons} on the INC1 data across machines~\label{tab:inc1}}
\end{table}

@@

\clearpage
\newpage
\subsection{INC1024}

@@

\clearpage
\newpage
\subsection{INC16384}

>>>>

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8} (plugged into the {\em bottom left} power strip) & INC1, INC16, INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb9}  (plugged into the {\em upper left} power strip)  & NC1, INC16, INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb10}  (plugged into the {\em upper left} power strip)  & NC1, INC16, INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb12}  (plugged into the {\em upper right} power strip)  & NC1, INC16, INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of the INC1, INC16, INC128 data used for histograms\label{tab:exp_notesINCs}}
\end{table}

\begin{table}[htp!]
\centering
{\small
 \begin{tabular}{|l|l|l|l|l||l|l|l|} \hline
 Task & Total & Process & Machine & Min (ms) & Max (ms) & Avg (ms) & \# of Iters\\ \hline
 INC1 &  1,000 & {\tt kslowd000} & {\tt sodb8} & 1 & 1 & 1 & 19 \\ \hline
 &   &  & {\tt sodb9} & 1 & 1 & 1 & 15 \\ \hline
 &   &  & {\tt sodb10} & 1 & 1 & 1 & 19 \\ \hline 
 \hline
  &  & {\tt kslowd001} & {\tt sodb8} & 1 & 1 & 1 & 15 \\ \hline
 &   &  & {\tt sodb9} & 1 & 1 & 1 & 18 \\ \hline
 &   &  & {\tt sodb10} & 1 & 1 & 1 & 15 \\ \hline 
 %&   &  & {\tt sodb12} & 1 & 1 & 1 & 19 \\ \hline 
%  \hline
 \end{tabular}
  }
 \caption{The statistics of the daemons on the INC1 data across machines~\label{tab:inc1}}
\end{table}

@@

%\clearpage
%\newpage
\subsection{INC1024}

@@

%\clearpage
%\newpage
\subsection{INC16384}
